detect patches

### 2024-01-31 scripts/classify_patches.Rmd
push framing to parkland

@@

abvi <- rast('../results/patches/Abronia_villosa.tif')

gd <- '/media/steppe/hdd/Geospatial_data'
hydr_bound <- rast( file.path(gd, 'WBD_rast', 'hu10R-line.tif') )

@@

  x <- terra::ifel(x > 0.75, 1, NA)
  x <- terra::mask(x, f_wbd, inverse = TRUE)
  landscape <- landscapemetrics::get_patches(x, directions = 4)
  calcs <- landscapemetrics::calculate_lsm(x, what = c('lsm_c_enn_mn', 'lsm_c_enn_cv',
                "lsm_p_enn", "lsm_p_enn", "lsm_p_cai", "lsm_p_para", "lsm_p_frac"), 
              neighbourhood = 4, directions = 4)

  p <- '../results/'
  write.csv(
    calcs[calcs$level == 'patch', c('id', 'metric', 'value')],
    filename = paste0(p, pout, '/', taxon, '-', 'patch_vals.csv'),  row.names = F
  )

  write.csv(
    calcs[calcs$level == 'class', c('id', 'metric', 'value')],
    filename = paste0(p, pout, '/', taxon, '-', 'class_vals.csv'), row.names = F
  )

@@

landscapR(f, pout = 'patch_metrics', pRout = 'fine_patches')

>>>>

```{r, eval = F}

@@

f <- list.files('../results/patches/')

gd <- '/media/steppe/hdd/Geospatial_data'
hydr_bound <- rast( file.path(gd, 'WBD_rast', 'hu12R-line.tif') )

@@

  taxon <- gsub('[.]tif', '', basename(x))
  x <- terra::rast(file.path('../results/patches', x))
  x <- terra::ifel(x > 0, 1, NA)
  x <- terra::mask(x, terra::crop(hydr_bound, x), inverse = TRUE)
  landscape <- landscapemetrics::get_patches(x, directions = 4)
  calcs <- landscapemetrics::calculate_lsm(x, what = c('lsm_c_enn_mn', 'lsm_c_enn_cv',
                "lsm_p_enn", "lsm_p_cai", "lsm_p_para", "lsm_p_frac"), 
              neighbourhood = 4, directions = 4)

  p <- '../results/'
  write.csv(
    calcs[calcs$level == 'patch', c('id', 'metric', 'value')],
    file = paste0(p, pout, '/', taxon, '-', 'patch_vals.csv'),  row.names = F
  )

  write.csv(
    calcs[calcs$level == 'class', c('metric', 'value')],
    file = paste0(p, pout, '/', taxon, '-', 'class_vals.csv'), row.names = F
  )

@@

lapply(f[4:20], FUN = landscapR, pout = 'patch_metrics', pRout = 'fine_patches')
